State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-03-29 draft.tex
Don't remember what changed.
what happened

[ticket: X]

%% Ticket list
\openTickets{Manuel:wlog,Manuel:invertability:assumption,Mark:log:bounds,Mark:proof:cor15,Manuel:proof:rewritten}

@@

Robust model predictive control (RMPC) is a control strategy for uncertain systems that optimises a 
performance objective for all possible realisations of model uncertainty.
%
First introduced in~\cite{Witsenhausen:1968}, the min-max RMPC problem is formulated as a sequence of games in which an adversary maximises the effect of model disturbances on a performance objective, and the controller solves the optimal
control problem for the resulting worst-case system.
%
We discuss the \emph{closed-loop setup} where, at each stage of a prediction horizon, the disturbance input maximizes the sum of the stage cost and the cost-to-go, and the control input minimises this cost so that the controller reacts to the worst-case disturbance at each stage.
%
The closed-loop setup includes, as a special case, the \emph{open-loop setup} in which the disturbance is allowed to perturb the 
entire trajectory before the controller is allowed to react, since this can be understood as a closed loop setup (with a horizon length of one) applied to a lifted system.
%

This paper considers the use of parametrised sets to bound model uncertainty. By allowing the bounds on model uncertainty to depend explicitly on the model state and control input we obtain a generalised framework for RMPC in which linearisation errors and multiplicative uncertainties can be modelled as additive disturbances.
%
General parametrised disturbance bounding sets were used in~\cite{Rakovic03,Rakovic06}; however, here we focus exclusively on problem formulations that lead to convex-concave min-max control problems.
% 
The paper's main contributions are to develop
%extends~\cite{Schaich:CDC:2015} by developing 
the analytical and computational tools that are needed to characterise and determine convex invariant and controllable sets for systems with parametrised uncertainty sets, and to employ these sets in a closed loop RMPC strategy. To this end, we provide necessary and sufficient conditions for the property, introduced in~\cite{Schaich:CDC:2015}, of \emph{parametric convexity}. We show that this condition is both necessary and sufficient to ensure that the corresponding robustly invariant and controllable sets are convex.

@@

We assume that $\mathcal V(x)$ is a piecewise affine parametrically convex 
%point-to-set map defined 
set defined as in~\eqref{eq:definition:PWA:polytopic:set:general}:
\begin{equation}\label{eq:definition:PWA:polytopic:set:cl}
\mathcal{V}(x) = \Bigl\{ v : a_i v \leq\max_{k} \{ b_{i,k} + c_{i,k} x\} \ \forall i \in\mathbb N_m\Bigr\} ,
\end{equation}
%
and that $\mathcal{X}$ is convex and polyhedral:
\begin{equation}\label{eq:definition:polytopic:X}
\mathcal{X}=\{x : \xi_i x \leq 1\ \forall i \in\mathcal{I}_{\mathcal{X}} \} 
\end{equation}
where $\boldsymbol{\xi}_{\mathcal{I}_{\mathcal{X}}}=\Xi$.
%
We further assume \todo{Manuel:wlog}{(without loss of generality)} that $\mathcal V(x)$ is compact for all finite $x\in\mathcal X$,
and can therefore be represented as the 
convex hull of its vertices: 
\begin{equation}\label{eq:definition:PWA:polytopic:set:vertices}
\mathcal V(x) = \conv\{v_j(x), \, j\in\mathbb{N}_q\} 
=  \conv\{\todo{Manuel:convHull}{\max_{k}}
\Theta_{j\todo{Manuel:convHull}{,k}} x + \theta_{j\todo{Manuel:convHull}{,k}},\, j\in\mathbb{N}_q\}.
\end{equation}
%
Here $v_j(x)$ is necessarily piecewise affine in $x$ for all $j\in\mathbb{N}_q$ since ${\mathcal{V}}(x)$ is piecewise affine in $x$.
%

>>>>

%% Ticket list
\openTickets{Manuel:convHull,Manuel:wlog,Manuel:invertability:assumption,Mark:log:bounds,Mark:proof:cor15,Manuel:proof:rewritten}

@@

Robust model predictive control (RMPC) is a control strategy for uncertain systems that optimises a 
performance objective for all possible realisations of model uncertainty.
%
First introduced in~\cite{Witsenhausen:1968}, the min-max RMPC problem is formulated as a sequence of games in which an adversary maximises the effect of model disturbances on a performance objective, and the controller solves the optimal
control problem for the resulting worst-case system.
%
We discuss the \emph{closed-loop setup} where, at each stage of a prediction horizon, the disturbance input maximizes the sum of the stage cost and the cost-to-go, and the control input minimises this cost so that the controller reacts to the worst-case disturbance at each stage.
%
The closed-loop setup includes, as a special case, the \emph{open-loop setup} in which the disturbance is allowed to perturb the 
entire trajectory before the controller is allowed to react, since this can be understood as a closed loop setup (with a horizon length of one) applied to a lifted system.
%
This paper considers the use of parametrised sets to bound model uncertainty. By allowing the bounds on model uncertainty to depend explicitly on the model state and control input we obtain a generalised framework for RMPC in which linearisation errors and multiplicative uncertainties can be modelled as additive disturbances.
%
General parametrised disturbance bounding sets were used in~\cite{Rakovic03,Rakovic06}; however, here we focus exclusively on problem formulations that lead to convex-concave min-max control problems.
% 
The paper's main contributions are to develop
%extends~\cite{Schaich:CDC:2015} by developing 
the analytical and computational tools that are needed to characterise and determine convex invariant and controllable sets for systems with parametrised uncertainty sets, and to employ these sets in a closed loop RMPC strategy. To this end, we provide necessary and sufficient conditions for the property, introduced in~\cite{Schaich:CDC:2015}, of \emph{parametric convexity}. We show that this condition is both necessary and sufficient to ensure that the corresponding robustly invariant and controllable sets are convex.

@@

We assume that $\mathcal V(x)$ is a piecewise affine parametrically convex 
%point-to-set map defined 
set defined as in~\eqref{eq:definition:PWA:polytopic:set:general}:
\begin{equation}\label{eq:definition:PWA:polytopic:set:cl}
\mathcal{V}(x) = \Bigl\{ v : a_i v \leq\max_{k} \{ b_{i,k} + c_{i,k} x\} \ \forall i \in\mathbb N_m\Bigr\} ,
\end{equation}
%
and that $\mathcal{X}$ is convex and polyhedral:
\begin{equation}\label{eq:definition:polytopic:X}
\mathcal{X}=\{x : \xi_i x \leq 1\ \forall i \in\mathcal{I}_{\mathcal{X}} \} 
\end{equation}
where $\boldsymbol{\xi}_{\mathcal{I}_{\mathcal{X}}}=\Xi$.
%
We further assume 
% \todo{Manuel:wlog}{(without loss of generality)} 
that $\mathcal V(x)$ is compact for all finite $x\in\mathcal X$,
and can therefore be represented as the 
convex hull of its vertices: 
\begin{equation}\label{eq:definition:PWA:polytopic:set:vertices}
\mathcal V(x) = \conv\{v_j(x), \, j\in\mathbb{N}_q\} 
=  \conv\{\todo{Manuel:convHull}{\max_{k}}
\Theta_{j\todo{Manuel:convHull}{,k}} x + \theta_{j\todo{Manuel:convHull}{,k}},\, j\in\mathbb{N}_q\}.
\end{equation}
%
Here $v_j(x)$ is necessarily piecewise affine in $x$ for all $j\in\mathbb{N}_q$ since ${\mathcal{V}}(x)$ is piecewise affine in $x$.
%
